User-customized hashtag/tag prediction on Twitter and StackOverflow:\protect \\ Comparing vector-based and ACT-R memory models of tag retrieval

### 2013-10-10 writeups/proposal/proposal.tex
foo
Former-commit-id: 2834c40ccf88f5633adb5c1937c780322c1e7385 [formerly ae44f790ffc678356de513b4e2be8662a2396fd4]
Former-commit-id: b06ef2714e97384db55acbba4240a22dcf2facf1

With vector-based systems, order information is included by creating an environment vector ($e_{bind(i,\Phi)}$) that is a function of environment vectors for both the word ($e_{i}$) and location ($\Phi$).
This function has the useful property that the resulting environment vector and the location vector can be inverted to return the original word's environment vector.
Convolution and inverse convolution (i.e., circular correlation) are used by \textcite{Plate1995} and \textcite{Jones2007} to implement these operations.
This allows for retrieval requests such as ``playing \#$\Phi$'', ``just read \#$\Phi$'', and ``vector-based $\Phi$ systems''.

>>>>

With vector-based systems, order information is included by creating an environment vector ($e_{bind(i,\Phi)}$) that is a function of environment vectors for both the word ($e_{i}$) and location ($\Phi$).
This function has the useful property that the resulting environment vector and the location vector can be inverted to return the original word's environment vector.
Circular convolution and inverse circular convolution (i.e., circular correlation) are used by \textcite{Plate1995} and \textcite{Jones2007} to implement these operations.
This allows for retrieval requests such as ``playing \#$\Phi$'', ``just read \#$\Phi$'', and ``vector-based $\Phi$ systems''.
